The Prevalence of E-Mail Header Injections on the World Wide Web

### 2016-05-23 System/components.tex
Finished edits to system section.

% Adam: This is where I am editing
\subsubsection{\Email Form Retriever}
\label{Comp:EMFR}
The \Email Form Retriever is the first stage in the Payload Injection module. It has the following important functions:
\begin{itemize}
	\item Retrieve the newly inserted forms in the \texttt{email\_forms} table, checking to ensure no duplication occurs before the fuzzing stage.
	\item Reconstruct each form, using the data stored in the \texttt{form} table, complete with input fields and their values.
	\item Construct the URL for the \texttt{action} attribute of the form so that we can send the HTTP request to the correct URL. 
\end{itemize}

\subsubsection{Fuzzer}
\label{Comp:Fuzzer}
The Fuzzer is the heart of the system and is the only component that interacts directly with the external websites. The Fuzzer is split into smaller modules, each of which is responsible for a particular type of fuzzing.  We inject payloads in two different stages, to improve the efficiency, and reduce the total number of HTTP requests we generate. This is because making HTTP requests is an expensive process~\cite{McGrath2009}, and can be a cause of bottlenecks in a Crawler-Fuzzer system~\cite{ShkapenyukTorstenSuel2001}.
The two different types of payloads we use for fuzzing are:
\paragraph{Non-Malicious Payload}
\label{Comp:Fuzzer:nmp}
The regular or non-malicious payload is a straight forward \Email address of the format -- \texttt{reguser(xxxx)@example.com}, where \texttt{xxxx} is replaced by our internal \texttt{form\_id}, to create a one-to-one mapping of the payloads to the forms, and \texttt{example.com} is replaced by the required domain.
This non-malicious payload allows us to check whether we can inject data into a form and whether we can overcome the `anti-bot' measures on the given website, without attempting to fuzz the website.

\paragraph{Malicious Payload}
\label{Comp:Fuzzer:mp}
In the malicious payload scenario, we inject the fields with the \texttt{bcc} (blind carbon copy) element. If the vulnerability is present, this will cause the server to send a copy of the \email to the \email address we added as part of the \texttt{bcc} field.

We consider a special case: the addition of a \texttt{x-check:in} header field to the payloads. This is due to Python's exhibited behavior when attaching
headers. Instead of overwriting a header if it is already present, it ignores duplicate headers. So, in case the \texttt{bcc} field is already present as part of the headers, our injected \texttt{bcc} header would be ignored. To overcome this, we need to inject a new header that is not likely to be generated by the web application. Hence, we inject our own \texttt{x-check:in} header to ensure we can get results if the injection was successful.

The malicious payloads consist of 4 different payloads. Each of these payloads is crafted for a particular use case. The four payloads are:

@@

	This is the most minimal payload, it injects a `newline' character followed by the \texttt{bcc} field.

@@

	This payload is added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the `Carriage Return - New Line (CRLF)' used on Windows systems.

@@

	As discussed above, the addition of the \texttt{x-check:in} header is to inject Python based websites.

@@

\end{enumerate}
The \texttt{xxxx} in all of the payloads is replaced by our internal \texttt{form\_id}, so as to create a one-to-one mapping of the payloads to the forms. The coverage provided by each payload is shown in Table~\ref{tab:payloadcov}.\\

\begin{table}[!htbp]
	\centering
	\begin{tabular}{|c|c|c|}
		\hline
		\multicolumn{1}{|c|}{\textbf{Payload}} & \multicolumn{1}{c}{\textbf{Languages covered}} & \multicolumn{1}{|c|}{\textbf{Platforms covered}}\\
		\hline
		1 & PHP, Java, Ruby, etc. & Unix\\
		\hline
		2 & PHP, Java, Ruby, etc. & Windows\\
		\hline
		3 & Python & Unix\\
		\hline
		4 & Python & Windows\\
		\hline
	\end{tabular}
	\caption[\titlecap{Payload coverage}]{Payload coverage, each payload covers a different platform/language.}
	\label{tab:payloadcov}
\end{table}
Along with the payload, the Fuzzer also injects data into the other fields of the form. This data must pass validation constraints on the individual input fields e.g.,\ for a name field, numbers might not be allowed. It is essential that the data we inject into the input fields adhere to the constraints. Our Fuzzer does this by making use of a `Data Dictionary' which has predefined `keys' and `values' for standard input fields such as \texttt{name}, \texttt{date}, \texttt{username}, \texttt{password}, \texttt{text}, and \texttt{submit}. The default values for these are generated on-the-fly for each form, based on generally followed guidelines for such fields. For example, password fields should consist of at least one uppercase letter, one lowercase letter, and a special character.

Once the data (including the payload) for the form is ready, the Fuzzer constructs the appropriate HTTP request (GET or POST) and sends the HTTP request to the URL that was generated by the \Email Form Retriever (Section~\ref{Comp:EMFR}).

\subsubsection{Injection Verification}
\label{Comp:EMA}
The Injection Verification module checks for the presence of injected data in the received \emails. This module works on the \emails received and stored by our Postfix server, and depending on the user who received the \email, it performs different functions.
\paragraph{Analyzing regular \email}
\sloppy
`Regular \email' refers to the \emails received by the \colorbox{lightgray}{\lstinline{reguser(xxxx)@example.com}} --- where \texttt{xxxx} is our internal \texttt{form\_id} --- that were sent due to injecting the `regular or non-malicious' payload (discussed in Section~\ref{Comp:Fuzzer:nmp}). The objective of the analysis on this \email is identify if the input fields that we injected with data appear on the resulting \email, and if so, which fields appear where.

To find this, we read through each received \email, and check whether \emph{any} of the fields we injected with data appear as part of either the headers or the body of the \email. If they do, we add them to the list of fields that can potentially result in an \ehi for the given \email. we then pass on this information back to the Fuzzer pipeline, along with the \texttt{form\_id}, so that the Fuzzer can now inject the malicious payloads into the same form.

\paragraph{Analyzing \email with payloads}
The `\emails with payloads' refer to \emails received by either the \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com}} or \colorbox{lightgray}{\lstinline{maluser(xxxx)@example.com}} accounts. These \emails were received due to injecting the malicious payloads that were discussed in Section~\ref{Comp:Fuzzer:mp}. Analysis of these \emails is considerably simpler than that of the regular \emails. This is due to the fact that this involves lesser processing of the contents of the \email compared to the previous section.
\paragraph{Detecting injected \texttt{bcc} headers}
As discussed in the payloads section~(\ref{Comp:Fuzzer:mp}), the payloads were crafted in such a way that the \emails received by \texttt{maluser} account directly indicate the presence of the injected \texttt{bcc} field. Thus, we simply parse the \emails and store them in the Database.

\label{analyze:detect_x_check}
\paragraph{Detecting injected \texttt{x-check} headers}
\Emails not received by the \texttt{maluser} account but by the \texttt{nuser} account constitute a special category of \emails.
These \emails could have been generated due to two reasons:
\begin{enumerate}
	\item The websites performed some sanitization routines and stripped out the \texttt{bcc} part of the payload, thereby sending \emails only to the \texttt{nuser} account. These \emails then act as proof that the vulnerability was not found on the given website.
	\item A more conducive scenario is when the \texttt{bcc} header was ignored for some reason, e.g.,\ Python's default behavior when it encounters duplicate headers. In this case, we check whether the \email contains the custom header \texttt{x-check}. If it does, then this is a successful exploit of the vulnerability, and we store it in the database.
\end{enumerate}

>>>>

\subsubsection{\Email Form Retriever}
\label{Comp:EMFR}
The \Email Form Retriever is the first stage in the Payload Injection module. It has the following functions:
\begin{itemize}
	\item Retrieve new forms and ensure no duplication occurs before the fuzzing stage.
	\item Reconstruct each form, using the stored form data, specifically the input fields and their values.
	\item Construct the target URL for the \texttt{action} attribute of the form to create an HTTP request to the correct URL for fuzzing. 
\end{itemize}

\subsubsection{Fuzzer}
\label{Comp:Fuzzer}
% Adam: we should call these something else but modules. We already have the top two modules, which are composed of components, now we need to split these into something (not components again).
The Fuzzer is the only component that interacts directly with the external web applications. The Fuzzer is split into smaller modules, each of which is responsible for a particular type of fuzzing.  The system injects payloads in two stages: the goal is to reduce the total number of HTTP requests the system generates to detect an \ehi vulnerability. Making HTTP requests is an expensive process~\cite{McGrath2009}, and can cause bottlenecks in a Crawler-Fuzzer system~\cite{ShkapenyukTorstenSuel2001}.
The two different types of payloads used for fuzzing are:
\paragraph{Non-Malicious Payload}
\label{Comp:Fuzzer:nmp}
The regular or non-malicious payload is simply an \email address. The goal is to see if the web application will send an \email message based on our input. The specific format of the \email is \texttt{reguser(xxxx)@example.com}, where \texttt{xxxx} is replaced by an internal id that uniquely maps the payload to the form, and \texttt{example.com} is replaced by our domain.

\paragraph{Malicious Payload}
\label{Comp:Fuzzer:mp}
After receiving an \email from a specific form, we then use the malicious payload to try to exploit an \ehi vulnerability. We inject the form parameters with the \texttt{bcc} (blind carbon copy) header. If the vulnerability is present, this will cause the server to send a copy of the \email to the \email address we added as the \texttt{bcc} field.

We consider a special case: the addition of an \texttt{x-check:in} header field to the payloads. This is due to Python's exhibited behavior when attaching
headers. Instead of overwriting a header if it is already present, Python will ignore duplicate headers. So, if the \texttt{bcc} field is already present as part of the headers, our injected \texttt{bcc} header would be ignored. To overcome this, we inject a new header that is not likely to be generated by the web application.

We created four different malicious payloads. Each of these payloads is crafted for a particular use case. The four payloads are:

@@

	This payload is the most minimal payload: it injects a newline character followed by the \texttt{bcc} field.

@@

	This payload is added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the ``Carriage Return - New Line (CRLF)'' used on Windows systems. %Adam: have a citation for this?

@@

	As discussed previously, the addition of the \texttt{x-check:in} header is to inject Python-based web applications.

@@

\end{enumerate}
The \texttt{(xxxx)} in each payload is replaced by an internal unique id to create a one-to-one mapping of the payloads to the forms.
% Adam: If we need to cut things for space, we can cut this next line and the payload coverage table.
The coverage provided by each payload is shown in Table~\ref{tab:payloadcov}.\\

\begin{table}[tbp]
	\centering
	\begin{tabular}{|c|c|c|}
		\hline
		\multicolumn{1}{|c|}{\textbf{Payload}} & \multicolumn{1}{c}{\textbf{Languages covered}} & \multicolumn{1}{|c|}{\textbf{Platforms covered}}\\
		\hline
		1 & PHP, Java, Ruby, etc. & Unix\\
		\hline
		2 & PHP, Java, Ruby, etc. & Windows\\
		\hline
		3 & Python & Unix\\
		\hline
		4 & Python & Windows\\
		\hline
	\end{tabular}
	\caption[\titlecap{Payload coverage}]{Payload coverage, each payload covers a different platform/language.}
	\label{tab:payloadcov}
\end{table}

Along with the payload, the Fuzzer also injects data into the other fields of the form. This data must pass validation constraints on the individual input fields (e.g.,\ for a name field, numbers might not be allowed). To maximize the amount of vulnerabilities the system discovers, the data injected into the input fields should adhere to the constraints. The Fuzzer uses a ``Data Dictionary'' which has predefined ``keys'' and ``values'' for standard input fields such as \texttt{name}, \texttt{date}, \texttt{username}, \texttt{password}, \texttt{text}, and \texttt{submit}.
% Adam: What does it mean here for these to be generated on-the-fly? Using templates?
The default values for these are generated on-the-fly for each form, based on generally followed guidelines for such fields. For example, password fields should consist of at least one uppercase letter, one lowercase letter, and a special character.
% Adam: can you add a sentence here about crawling and fuzzing fields on the web is an open problem (and cite ``Crawling the hidden web''

When the fuzzed data is ready, the Fuzzer constructs the appropriate HTTP request (GET or POST) and sends the HTTP request to the URL that was generated by the \Email Form Retriever (Section~\ref{Comp:EMFR}).

\subsubsection{Injection Verification}
\label{Comp:EMA}
The Injection Verification module checks for the presence of injected data in the received \emails. This module works on the \emails received and stored by our Postfix server, and, depending on the user account that received the \email, it performs different functions.
\paragraph{Analyzing regular \email}
\sloppy
`Regular \email' refers to the \emails received by account \colorbox{lightgray}{\lstinline{reguser(xxxx)@example.com}} that were sent due to injecting the regular, non-malicious, payload (discussed in Section~\ref{Comp:Fuzzer:nmp}). The objective of the analysis on this \email is identify if the input fields that we injected with data appear on the resulting \email, and if so, which fields appear where.

To find this, we parse each received \email, and check whether \emph{any} of the fields we injected with data appear as part of either the headers or the body of the \email. If they do, we add them to the list of fields that can potentially result in an \ehi vulnerability for the given \email. We then pass on this information back to the Fuzzer pipeline, along with the vulnerable form.

\paragraph{Analyzing \email with payloads}
The ``\emails with payloads'' refers to \emails received by either the \colorbox{lightgray}{\lstinline{nuser(xxxx)@example.com}} or \colorbox{lightgray}{\lstinline{maluser(xxxx)@example.com}} accounts. These \emails could only be received as a result of injecting the malicious payloads that were discussed in Section~\ref{Comp:Fuzzer:mp}.

\paragraph{Detecting injected \texttt{bcc} headers}
As discussed in the payloads section~(\ref{Comp:Fuzzer:mp}), the payloads were crafted such that the \emails received by the \texttt{maluser} account directly indicate the presence of the injected \texttt{bcc} field.

\label{analyze:detect_x_check}
\paragraph{Detecting injected \texttt{x-check} headers}
\Emails not received by the \texttt{maluser} account but by the \texttt{nuser} account constitute a special category of \emails.
These \emails could have been generated due to two reasons:
\begin{enumerate}
	\item The web application performed some sanitization routines and stripped out the \texttt{bcc} part of the payload, thereby sending \emails only to the \texttt{nuser} account. These \emails then act as proof that the vulnerability was not found on the given URL.
	\item The \texttt{bcc} header can be ignored for other reasons (e.g.,\ Python's default behavior when it encounters duplicate headers). In this case, we check if the \email contains the custom header \texttt{x-check}. If it does, then this is a successful exploit of the vulnerability.
\end{enumerate}
